Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 Discussion-Proof.tex
addressed the issue in Theorem 10
my late nite attempt to fix thm 9

\begin{rtheorem}{Theorem}{\ref{rst:discrete}}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment budget bounded above by 
\begin{align*}
\pfedit{
O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot
    \max\bigg\{\frac{2}{p},
    \left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2}
    \bigg\}
\right)
}
\end{align*}
and expected regret bounded above by 
\begin{align}
O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
  \right).  \nonumber
\end{align}
\end{rtheorem}

\begin{proof}
The proof of the expected payment bound is the same as the proof of Theorem~\ref{rst:budget}, except that we now define $h(\ell) := \max \left( \frac{2}{\MinProb},
\pfedit{
\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
}
\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
\right)
\pfedit{
= 
\max \left( \frac{2}{\MinProb},
\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2}
\right)
}
$.

To prove the bound on the expected regret, one can first prove tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
which replace the $\exp(2/\MinProb)$ term with simply $2/\MinProb$.
In return, the length of phase $s$ is now bounded only be $\ARMNUM s$ instead of $\ARMNUM \log(s)$.
Substituting these changes into the proof\pfedit{s} of Theorem\pfedit{s}~\ref{rst:regret} \pfedit{and \ref{rst:budget}}, we obtain the claimed bounds.

@@

>>>>

\begin{rtheorem}{Theorem}{\ref{rst:discrete}}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment budget bounded above by 
\begin{align*}
\pfedit{
O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot
    \max\bigg\{\frac{2}{p},
    \left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2}
    \bigg\}
\right)
}
\end{align*}
and expected regret bounded above by 
\pfedit{
\begin{align*}
O \left(
\ARMNUM \MAXR \left(
	\frac2{\MinProb}
       + \frac{\log^2(T) \Diam^4 d^4 \sigma^4}{\hat{z}^4}\right) \right)
\end{align*}
}
\end{rtheorem}

\begin{proof}
The proof of the expected payment bound is the same as the proof of Theorem~\ref{rst:budget}, except that we now define $h(\ell) := \max \left( \frac{2}{\MinProb},
\pfedit{
\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
}
\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
\right)
\pfedit{
= 
\max \left( \frac{2}{\MinProb},
\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2}
\right).
}
$
%\pfedit{and $s_1 = \max(2,\frac{30\sigma^3}{x^3}, \frac2{\MinProb})$}.

To prove the bound on the expected regret, one can first prove tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
which replace the $\exp(2/\MinProb)$ term with simply $2/\MinProb$.
In return, the length of phase $s$ is now bounded only by $\ARMNUM s$ instead of $\ARMNUM \log(s)$.
Substituting these changes into the proof of Theorem~\ref{rst:regret}, we obtain the claimed bounds.

@@

\pfcomment{
The calculation I did for the bound on the regret is:

\begin{itemize}
\item regret from times when we pay is $RN\frac2p$
\item regret from times with $\gamma(s) >= \hat{z}$ is $NR \log^2(T) D^4 d^4 sigma^4 / \hat{z}^4$
\item regret from small regret is 0
\item regret from big regret is $NRd/T$
\end{itemize}

Total is NR ($\frac2p + \frac{d}{T} + \frac{\log^2(T) D^4 d^4 sigma^4}{zhat^4}$)
}
